To Airbnb?: A Question of Revenue

### 2018-05-31 papers/full_paper.Rmd
Add: Abstract

>>>>

```
## Abstract

The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").  In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one. We also find that hosting policies matter, suggesting that even the right property needs the right owner(s) to make short-term rental the more profitable approach.
